\documentclass[letterpaper,10pt]{article}
\usepackage[top=0.75in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}

\usepackage{graphicx}                                        
\usepackage{amssymb}                                         
\usepackage{amsmath}                                         
\usepackage{amsthm}                                          

\usepackage{alltt}                                           
\usepackage{float}
\usepackage{color}
\usepackage{url}

\usepackage[TABBOTCAP, tight]{}
\usepackage{enumitem}

\usepackage{geometry}
\geometry{textheight=8.5in, textwidth=6in}

%random comment

\newcommand{\cred}[1]{{\color{red}#1}}
\newcommand{\cblue}[1]{{\color{blue}#1}}

\usepackage{hyperref}
\usepackage{geometry}

\begin{document}
    \begin{titlepage}
    \newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
    \center 
    \textsc{\Large cs 461 fall term}\\[0.5cm] 
    \textsc{\Large capstone}\\[0.5cm] 
    \HRule \\[0.4cm]
    { \huge \bfseries Website and Application for Health Sciences Careers in Oregon }\\[0.5cm] % Title of your document
    \HRule \\[1.5cm]
    \begin{minipage}{0.4\textwidth}
        \begin{flushleft} \large
        \emph{Authors:}\\
          Jason Ye, David Corbelli, Zixuan Feng \linebreak
        \end{flushleft}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
        \begin{flushright} \large
        \emph{Instructors:} \\
        D. Kevin McGrath
		\\
        Kirsten Winters
        \end{flushright}
    \end{minipage}\\[2cm]
    \begin{abstract}
    \item
The application and website for Oregon Health Science Careers is a guide for middle school and high school level students to learn about health science careers. 
Between an application and website, the service shall provide information as exploration tool for students looking for future careers in health science. 
Due to the many fields under the classification of health and science, it may be difficult for a student beginning to take an interest in the subject to find the proper path they’re looking for. 
As a development team we will focus on developing an exploratory website and then develop corresponding applications for two major platforms, Android and iOS.
Through our platform, students will explore pathways and careers in health and science. 
In this paper, we will discuss our design and specifications of the applications and website we plan to develop. 
    \end{abstract}
   

    \end{titlepage}
    


    %%%%%%%%%%%%%%%%Abstract Done%%%%%%%%%%%%%%%%%%%%
  \section {Problem Statement}	
    \paragraph {Problem Definiton}
At the middle school and high school level, students begin taking an interest in their future career paths. 
For many, it remains unclear how to take first steps towards their future careers and what requirements they will need to fulfill.
Within the field of health and sciences, there exist many branching paths to explore before making an informed definitive choice can be made; the major umbrellas of health sciences include therapeutic services, diagnostics, health informatics, support services, as well as research and development. 
Each each of these departments separate and divide further into more specific fields. 
It is important that students are able to distinguish between the different fields in order to make an educated choice and without an organized platform it may be difficult for students to identify which option is most suited for them. 



    %%%%%%%%%%%%%%%%%%Problem Definition%%%%%%%%%%%%%%%%%%%%%

 \paragraph {Problem Solution}
In order to bridge this gap in information, we shall build a website with the purpose of education and career path exploration that will allow students, along with their parents, teachers, and counselors, to develop an understanding of what each career option encompasses.
This area of the site will detail information specifying the differences between classifications of health services and what duties can be expected of an individual in such a position.  
Informative pages pertaining to career paths will branch into increasingly specific fields  in order for students to pinpoint their options. 
Along with career exploration, we will also open up navigation and development for pages such as information on health education centers, workforce partners, educators, and current events news. 
For convenience, we will also develop a mobile app counterpart with information linked to the website that allows the capability to bookmark specific pages for later viewing.
With this platform, students will have the information required to pursue a career in health sciences.



    %%%%%%%%%%%%%%%%%%%%%%%%%%%%Problem solution%%%%%%%%%%%%%%%%%%%%

 \paragraph {Performance metrics}

In order to measure our work, we need to know what is working and what is not for both the website and our applications. Towards this end, we will provide a website and application prototype for user-based testing. The prototype would allow us to examine and analyze our objective: whether or not we can assist students in finding a field in health sciences that interests them. We would be collecting and testing feedback to see which information is useful and which is not for our audience. One of the testing we will be using is script testing. Script testing will help discover problems in our design. It is important for us to know whether or not the user can find or access a certain feature on the website and application given certain scenarios. These tests tend to produce benefits for usability metrics and generate qualitative data. Our goal is to provide a user-friendly way for students to explore different career paths, thus ensuring a quality user-interface is necessity. Once we have completed development and our user-tests return all positive experiences we may conclude that we have reached our goal.

        


    
\end{document}